A Quantitative Genetic Linked Selection Model fit to the Negative Selection Process in Humans

### 2023-07-06 manuscript/manuscript.tex
ms changes

\section*{Results}

@@

\subsection*{Application to Humans and Model Comparison}

Our composite likelihood method takes tracks of annotated features (an
``annotation model") that are \emph{a priori} expected to have similar fitness
effects, and estimates the overall mutation rate and distribution of fitness
effects for each feature type. We consider two classes of annotation models:
(1) CADD score models, which assign a rank-order pathogenicity score to each
basepair, and (2) and more interpretable gene feature-based models that
includes protein coding regions, intron and UTRs, and PhastCons regions. We
include PhastCons regions because there is abundant evidence of
highly-conserved non-coding regions in humans under negative selection
\parencite{Meader2010-hm,Harmston2013-tt,Katzman2007-gq,Siepel2005-wh}, but
would not be included in gene-based annotation. Since our method fits a DFE for
each feature type, PhastCons regions that overlap other gene annotations (e.g.
coding sequences) must be assigned to either of the two feature types. Since
this can impact estimates, we fit both alternatives: a PhastCons Priority
model, where genic features that overlap PhastCons regions are classified as
PhastCons, and a Feature Priority model, where gene structure features take
priority and the PhastCons type catches all highly-conserved non-genic regions.
In total, we fit four annotation models (CADD 6\%, CADD 8\%, PhastCons
Priority, and Feature Priority) to high-coverage 1000 Genome data for three
populations: Yoruba (YRI), Han Chinese (CHB), and European (CEU) reference
samples. We assess and compare our models according to how well they predict
patterns of diversity on whole chromosomes left-out during the model fitting
process (e.g. leave-one-chromosome-out, LOCO). We use the metric
$R_\text{LOCO}^2$, which is the proportion of the observed variance in genomic
diversity at the megabase scale predicted by our model. We experimented with a
few smaller spatial scales, but our results were consistent with previous
results suggesting the human linked selection signal fits best at the megabase
scale \parencite{Murphy2022-sj}.

@@

Overall, we find the PhastCons Priority and CADD 6\% models fit about equally
as well (Figure \ref{fig:figure-2}A), explaining $R^2=68.45$\% and
$R^2=68.04$\% of the out-sample variance in Yoruba pairwise diversity at the
megabase-scale, respectively. Generally, our models predict out-sample
diversity levels slightly better than previous methods; the best-fitting CADD
6\% model from \textcite{Murphy2022-sj} explained 60\% of diversity in left-out
2 Mbp windows across YRI samples.

In populations impacted by the out-of-Africa bottleneck, the goodness-of-fit
was lower across all models (e.g. 62.98\% and 59.98\% for CEU and CHB
respectively in the PhastCons Priority model). Our PhastCons Priority model
fits marginally better than the CADD 6\% model consistently across all three
populations (Supplementary Table \ref{supp:tbl-r2}). This is likely because the
PhastCons Priority model has more DFE parameters, and thus can fit finer-scale
differences with the four feature types. By contrast, the CADD 6\% track must
fit patterns of diversity to conserved sites under a single DFE. The CADD 8\%
model fit slightly worse than the CADD 6\% across all populations, and the
Feature Priority model had the poorest-fit.

Since our method is built upon theory that fixes the weak selection problem of
classic BGS theory, it should in principle fit equally well when an annotation
model includes regions that are under no selective constrain and neutrally
evolving. To test this, for each annotation model (which are ``sparse") we fit
a corresponding ``full" model that assigns the remaining complement of the
genome as a feature called ``other". This category contains most of the genome,
and is likely to be predominantly neutrally evolving. Ideally, the
goodness-of-fit of model using our B' method should be invariant to whether an
annotation model is sparse or full. Indeed, we find this to be the case: both
in-sample $R^2$ and out-sample $R_\text{LOCO}^2$ values are nearly identical
across full and sparse-track models (Figures \ref{fig:figure-2}A and
\ref{fig:figure-2}B, round points).

By contrast, full annotation models fit poorly when using classic BGS theory
(Figure \ref{fig:figure-2}B, diamond-shaped points) and lead to unreasonable
parameter estimates (discussed below). Additionally, when sparse annotation
models contain genomic features that are likely under weak constraint (such as
introns and UTRs), models fit worse under classic BGS theory than our B' method
(Figure \ref{fig:figure-2}A). However, among the CADD annotation models, the
goodness-of-fit is nearly identical between B' and classic BGS methods. This
behavior is what we would expect given that the CADD annotation models contain
only the most pathogenic sites, which are \emph{a priori} very likely under the
strong selection domain under which B' and classic BGS theory agree.

Overall, our $R_\text{LOCO}^2$ estimates suggest our negative selection model
explains up to 68\% of out-sample variance in diversity of the megabase scale,
even though our method assumes constant demography and homogeneous mutation
rates along the genome. A worthwhile question is: how much variation
\emph{could} we expect to fit at this scale? Given that selection alters
genealogies in ways beyond just decreasing mean pairwise coalescence time and
populations have non-constant demography, an exact analytic answer is
intractable. However, we can get an approximate idea if we assume that the
residual variance $\sum_b (\pi_b - \widehat{\pi}_b)^2$ is determined entirely
by the expected neutral coalescence noise around the expected coalescence time
$2B(b)N$ (see Method XXX). Thus, we define $R_\text{coal}^2$ as the theoretic
proportion of variance explainable under this model to ballpark the variance
capable of being explained.

We find that our out-sample $R_\text{LOCO}^2$ for the Yoruba samples
($R_\text{LOCO}^2 \approx 68$\%) is slightly above the theoretic
$R_\text{coal}^2 \approx 67$\%. This suggests our model is in the vicinity of
fitting all possible signal possible under these simplifying assumption. It
should be noted that selection is expected to \emph{decrease} the variance in
coalescence times beyond simply rescaling effective population size implies;
better future models for $R_\text{coal}^2$ could show there is more linked
selection signal to explain.

For bottlenecked out-of-Africa populations, we find a larger discrepancy
between $R_\text{coal}^2$ and observed out-sample $R_\text{LOCO}^2$. The
theoretic $R_\text{coal}^2 \approx 64$\% for both populations, compared to the
observed $R_\text{LOCO}^2 \approx 62$\% for CEU and $R_\text{LOCO}^2 \approx
59$\% for CHB. Given that bottlenecks would act to increase the residual
variance in coalescence times beyond the level implied by the effective
population size, the gap would likely shrink under more realistic models or
simulation-based approximations for $R_\text{coal}^2$. Overall, this suggests
that negative selection models explain the vast majority coalescence time
variation at the megabase-scale that is capable of being explained (i.e. that
is not coalescence noise).

\subsection*{Estimates of the Distribution of Fitness Effects in Humans}

@@

Our composite likelihood method has three sets of parameters: expected
diversity in the absence of linked selection diversity $\pi_0$, the mutation
rate $\mu$, and the distribution of fitness effects $\mathbf{W}$ across the
selection grid for each of the $K$ feature types. Given that the relationship
between $\pi$ and the strength selection is U-shaped, we wondered whether the
observed genome-wide patterns of diversity could be explained by weaker
selection than found in previous methods based on classic BGS theory.

However, across all of our annotation models, new deleterious mutations in
likely conserved features are consistently estimated to have strongly
deleterious effects (Figure \ref{fig:figure-3}A) consistent with previous work
\parencite{McVicker2009-ax,Murphy2022-sj}. This includes features such as
coding sequences, PhastCons regions, or the top 6\% of basepairs with the most
pathogenic CADD scores. However, we find that there is considerable uncertainty
in how strong selection is against the most deleterious mutations. For example,
in the CADD 6\% full-track model, new mutations are estimated to have a
selection coefficients of $s = 10^{-1}$ with 42\% chance, $s=10^{-2}$ with
7.8\% chance, and $s=10^{-3}$ with 41\% chance. These estimates suggest a
bimodal DFE (Figure \ref{fig:figure-3}A, second row, left column), and are
mirrored across the other CADD models.

Given that previous methods have typically not estimated the DFE up to
selection coefficients of $s=10^{-1}$, we ran additional models using a DFE
constrained to $s=10^{-2}$. Each of these constrained-DFE models across all
populations fit the data less well than models run with the grid up to
$s=10^{-1}$, explaining 1\% less of the leave-one-chromosome-out variation on
average. As expected, the constrained-DFE models put more mass on $s=10^{-2}$
(see Supplementary Table \ref{supp:tbl-r2}). Overall, this common behavior
across models seems likely to reflect a non-identifiability issue between
selective effects of $s=10^{-1}$ and $s=10^{-2}$, which we refer to as the
\emph{strong-selection non-identifiability} issue.

We propose that one mechanism for this non-identifiability is that mutations
extremely harmful to fitness are difficult to distinguish from a smaller
effective population. Intuitively, as $s$ increases, the average persistence
time (in generations) of the mutation in the population goes below one
generation, i.e. death of the carrier of the \emph{de novo} mutation. In this
hypothetical limit, each occurrence of a very harmful mutation is like an
instantaneous death and thus acts like a genome-wide reduced effective
population size. In our model, this genome-wide effective population size is
parameterized by $\pi_0$; thus, one line of evidence for this effect is a
correlation between estimates of $\pi_0$ and average selection $\bar{s}$.
Looking at the CADD 6\% models fit across the default and constrained DFE
grids, we find this is the case. Across every population, average selection was
about 7 times larger using the default grid, and $\pi_0$ was $5.6\%$ larger.
There was no similar consistent change in mutation rate estimates among
populations. In the CADD 6\% model, genome-wide average reduction factor
$\bar{B}$ was $\approx 6.1\%$ lower in the default versus constrained grid.
Overall, this suggests that the linked selection signal alone carries little
information that can differentiate very strong selection from a slightly
smaller drift-effective population size.

Despite the strong-selection non-identifiability issue, we still were curious
how stable these estimates are across samples from reference populations. In
particular, we focused on the Feature Priority model, which fits the data less
well but is more interpretable since its annotation is based on gene features.
Overall, estimates of the distribution of selection coefficients are stable
across populations and had narrow uncertainty as estimated by a block jackknife
procedure (Figure \ref{figure-3}B). Coding sequences show the strong-selection
non-identifiability issue, and an uncertain signal of a neutral mode in the
DFE. This would be expected given the very different levels of selective
constraint synonymous and non-synonymous sites in coding sequences are under.
The PhastCons class of this Feature Priority model, which contains highly
conserved non-coding elements (XXX), is under strong selective constraint as
expected. Interestingly, in our PhastCons Priority annotation model (Figure
\ref{fig:figure-3}A bottom row), the DFE estimate for coding sequences
excluding PhastCons regions is neutral. This is expected; the selection signal
in coding regions is absorbed by the PhastCons feature.

@@

Early genome-wide models of background selection closely fit megabase-scale
patterns in sequence divergence among five primates
\parencite{McVicker2009-ax}. However, the mutation rate estimates from this
model were unreasonably high compared to pedigree-based estimates (XXX). This
mutation rate discordance has led to the hypotheses that positive selection
could explain some fraction of the genome-wide linked selection signal (e.g.
\cite{Enard2014-kz}); however, evidence suggests that the role of classic
sweeps in humans is minuscule
\parencite{Pickrell2009-tt,Hernandez2011-gs,Murphy2022-sj}. Furthermore, Murphy
et al. find the classic BGS model fit using the CADD 6\% track leads to
mutation rate estimates that are consistent with pedigree-based rates. Given
that our method is based on a different theoretic approach, we curious whether
it would lead to estimates consistent with pedigree-based mutation rates.

Across all populations, our mutation rate estimates from CADD-based models are
roughly concordant with pedigree-based estimates (Figure \ref{fig:figure-4}A).
Our full-track CADD 6\% model estimates the mutation rate as $\widehat{\mu} =
1.46 \times 10^{-8}$ for YRI, $1.53 \times 10^{-8}$ for CEU, and $1.5 \times
10^{-8}$ for CHB reference samples (Supplementary Table \ref{supp:tbl-r2}). As
expected, the sparse-track CADD model mutation rate estimates are identical
between the B' and classic BGS methods (Figure \ref{fig:figure-4}A top row).

However, mutation rate estimates for feature-based annotation models show
several issues. First, mutation rate estimates under using our implementation
of classic BGS theory are an order of magnitude below the expected range
(Figure \ref{fig:figure-4}A top row). We observe similar behavior when we use
the classic BGS model to fit full-coverage annotation models (Figure
\ref{fig:figure-4}A bottom row). This behavior is consistent with the fact that
classic BGS theory cannot fit weak selection, and to accommodate features under
weak constrain (e.g. introns, UTRs, and the ``other" feature) it must severally
underestimate the mutation rate.

Second, we noticed that across all populations and sparse/full tracks, the CADD
6\% model consistently led to slightly higher mutation rates than the CADD 8\%
model (Figure \ref{fig:figure-4}A bottom row; Supplementary Table
\ref{supp:tbl-r2}). This pattern was observed in Murphy et al. too (2023;
Appendix 1, Figure 16). This behavior is consistent with a non-identifiability
issue between a slightly higher per-basepair mutation rate and annotation
tracks that contain more conserved sequence. This is expected from theory,
since both classic BGS and SC16 models only depend on mutation rate through the
compound parameter $\mu L$ where $L$ is the length of the conserved segment.
Even though our method is much more robust to including non-conserved regions
like introns, we still observe this non-identifiability issue.

>>>>

\section*{Results: Confirmation of Theory}

@@

\section*{Results: Application to Human Genomic Data}

\subsection*{Annotation Model Comparison}

Our composite likelihood method takes tracks of annotated features (an
``annotation model") that are \emph{a priori} expected to have similar fitness
effects, and estimates the overall mutation rate and distribution of fitness
effects for each feature type. We consider two classes of annotation models:
(1) CADD-based models, which consider the top $x\%$ of basepairs according to
the CADD pathogenicity score assigned to each basepair, and (2) and more
interpretable gene feature-based models that includes protein coding regions,
intron and UTRs, and PhastCons regions. We include PhastCons regions because
there is strong evidence of highly-conserved non-coding regions
\parencite{Meader2010-hm,Harmston2013-tt,Katzman2007-gq,Siepel2005-wh}, that
would be missed by gene feature only annotation. These two classes of
annotation models have a trade-off between fine-scaled specificity to which
basepairs are likely to be under negative selection, and interpretability of
the DFE estimates for each feature.

Our method estimates the distribution of fitness effects (DFE) for each feature
class. While CADD-based models only have a single conserved feature class (e.g.
CADD 6\%), feature-based models can have multiple feature classes under varying
levels of selective constrain. However, overlapping features (e.g. a basepair
that is annotated as both PhastCons and coding sequence) must be assigned to
one category or the other. Since this assignment impact DFE estimates, we fit
both of the two alternatives. First, a \emph{PhastCons Priority} model, where
genic features that overlap PhastCons regions are classified as PhastCons, and
all remaining coding basepairs are labeled as CDS. Second, a \emph{Feature
Priority} model, where all coding basepairs are assigned to CDS, and the
PhastCons class catches the remaining highly-conserved non-genic regions.

In total, we fit four annotation models (CADD 6\%, CADD 8\%, PhastCons
Priority, and Feature Priority) to high-coverage 1000 Genome data for three
populations: Yoruba (YRI), Han Chinese (CHB), and European (CEU) reference
samples. We assess and compare our models according to how well they predict
patterns of diversity on whole chromosomes left-out during the model fitting
process (e.g. leave-one-chromosome-out, LOCO). We use the metric
$R_\text{LOCO}^2$, which is the proportion of the observed variance in genomic
diversity at the megabase scale predicted by our model. We experimented with a
few smaller spatial scales (e.g. 100 kbp), but our results were consistent with
previous results suggesting the human linked selection signal fits best at the
megabase scale \parencite{Murphy2022-sj}.

@@

Overall, we find the PhastCons Priority and CADD 6\% models fit about equally
as well (Figure \ref{fig:figure-2}A), consistent with recent work using classic
BGS theory \parencite{Murphy2022-sj}. However, we find that our models predict
out-sample diversity levels slightly better than previous methods. For these
two models, we find that our B' method predicts $R_\text{LOCO}^2=68.45$\% and
$R_\text{LOCO}^2=68.04$\% of the out-sample variance in Yoruba pairwise
diversity at the megabase-scale, respectively. By contrast, the best-fitting
CADD 6\% model from \textcite{Murphy2022-sj} explained 60\% of diversity in
left-out 2 Mbp windows across YRI samples. We note that this might be explained
by other differences in data process, reference genome, etc.

In populations impacted by the out-of-Africa bottleneck, the goodness-of-fit
was lower across all models (e.g. 62.98\% and 59.98\% for CEU and CHB
respectively in the PhastCons Priority model). Our PhastCons Priority model
fits marginally better than the CADD 6\% model consistently across all three
populations (Supplementary Table \ref{supp:tbl-r2}). This is likely because the
PhastCons Priority model has more DFE parameters, and thus can fit finer-scale
differences among the four feature types. By contrast, the CADD 6\% track must
fit patterns of diversity to conserved sites under a single DFE. The CADD 8\%
model fit slightly worse than the CADD 6\% across all populations, and the
Feature Priority model had the poorest-fit.

Since our method is built upon theory that fixes the weak selection problem of
classic BGS theory, it should in principle fit equally well when an annotation
model includes regions that are under no selective constraint and thus
neutrally evolving. To test this, for each of our annotation models (which are
``sparse") we fit a corresponding ``full" model that assigns the remaining
complement of the genome to a feature called ``other" that contains most of the
genome. Ideally, how a model fits using our B' method should be invariant to
whether an annotation model is sparse or full, since our method in principle
can accommodate weak selection and neutrality. Indeed, we find this to be the
case: both in-sample $R^2$ and out-sample $R_\text{LOCO}^2$ values are nearly
identical across full and sparse-track models (Figures \ref{fig:figure-2}A and
\ref{fig:figure-2}B, round points).

By contrast, full annotation models fit poorly under classic BGS theory (Figure
\ref{fig:figure-2}B, diamond-shaped points) and lead to unreasonable parameter
estimates (discussed in Section XXX). Additionally, when sparse annotation
models contain genomic features that are likely under weak constraint (such as
introns and UTRs), models fit worse under classic BGS theory than our B' method
(Figure \ref{fig:figure-2}A). However, among the CADD annotation models, the
goodness-of-fit is nearly identical between B' and classic BGS methods. This
behavior is what we would expect given that the CADD models contain only the
most pathogenic sites, which are \emph{a priori} very likely under the strong
selection domain under which B' and classic BGS theory agree.

Overall, our $R_\text{LOCO}^2$ estimates suggest our negative selection model
explains up to 68\% of out-sample variance in diversity of the megabase scale,
even though our method assumes constant demography and homogeneous mutation
rates along the genome. A worthwhile question is: how much variation
\emph{could} we expect to fit at this scale? Given that selection alters
genealogies in ways beyond just decreasing mean pairwise coalescence time and
populations have non-constant demography, an exact analytic answer is
intractable. However, we can get an approximate idea if we assume that the
residual variance $\sum_b (\pi_b - \widehat{\pi}_b)^2$ is determined entirely
by the expected neutral coalescence noise around the expected coalescence time
$2B(b)N$. This can be be found analytically, plugging-in our predictions for
$B(b)$. This allows us to calculate $R_\text{coal}^2$ to ballpark the theoretic
variance that is capable of being explained, assuming this coalescence-only
noise process (see Method XXX). We note that selection is expected to
\emph{decrease} the variance in coalescence times beyond a rescaled effective
population size implies; our $R_\text{coal}^2$ would be an underestimate under
selection.

We find that our out-sample $R_\text{LOCO}^2$ for the Yoruba samples
($R_\text{LOCO}^2 \approx 68$\%) is slightly above the theoretic
$R_\text{coal}^2 \approx 67$\%. This suggests our model is close to the
vicinity of fitting all the signal possible, under the coalescence-only noise
assumption. By contrast, for bottlenecked out-of-Africa populations, we find a
larger discrepancy between $R_\text{coal}^2$ and observed out-sample
$R_\text{LOCO}^2$. The theoretic $R_\text{coal}^2 \approx 64$\% for both
populations, compared to the observed $R_\text{LOCO}^2 \approx 62$\% for CEU
and $R_\text{LOCO}^2 \approx 59$\% for CHB. Given that bottlenecks would act to
increase the residual variance in coalescence times beyond the level implied by
the effective population size, the gap would likely shrink under more realistic
models or simulation-based approximations for $R_\text{coal}^2$. Overall, this
suggests that negative selection models explain the vast majority coalescence
time variation at the megabase-scale that is capable of being explained (i.e.
that is not coalescence noise).

\subsection*{Estimated Distribution of Fitness Effects}

@@

Our composite likelihood method has three sets of parameters: expected
diversity in the absence of linked selection diversity $\pi_0$, the mutation
rate $\mu$, and the distribution of fitness effects $\mathbf{W}$ across the
selection grid for each of the $K$ feature types. Given that the relationship
between $\pi$ and the strength selection is U-shaped, our model in theory could
fit under different combinations of parameters.

However, across all of our annotation models, new deleterious mutations in
conserved feature classes were consistently estimated to have strongly
deleterious effects (Figure \ref{fig:figure-3}A), consistent with previous work
\parencite{McVicker2009-ax,Murphy2022-sj}. This includes features such as
coding sequences, PhastCons regions, or the top 6\% of basepairs with the most
pathogenic CADD scores. However, we find that there is considerable uncertainty
in how strong selection is against the most deleterious mutations. For example,
in the CADD 6\% full-track model, new mutations are estimated to have a
selection coefficients of $s = 10^{-1}$ with 42\% chance, $s=10^{-2}$ with
7.8\% chance, and $s=10^{-3}$ with 41\% chance. This creates a bimodal DFE
(Figure \ref{fig:figure-3}A, second row, left column), which is mirrored across
the other CADD models. Moreover, these DFE estimates suggest a very high
average selection coefficient across CADD 6\% regions of $\wisehat{\bar{s}}
\approx 0.038$.

Given that previous methods have typically not estimated the DFE up to
selection coefficients of $s=10^{-1}$, we ran additional ``constrained grid"
models using a DFE only up to $s=10^{-2}$. Across all populations, these
constrained grid models fit the data less well than the default grid. On
average, the constrained grid fits had $R_\text{LOCO}^2$ one percentage point
lower (see Supplementary Table \ref{supp:tbl-r2}). As expected, the constrained
grid models distributed mass onto the next strongest selection coefficient,
$s=10^{-2}$. While the DFE could be truly bimodal for highly-conserved regions
with a very high average selection coefficient, a likely alternative is that
these results reflect a non-identifiability issue between selective effects of
$s=10^{-1}$ and $s=10^{-2}$. We will refer to this as the
\emph{strong-selection non-identifiability} issue.

We propose that one mechanism for this non-identifiability is that mutations
extremely harmful to fitness are difficult to distinguish from a smaller
effective population. Intuitively, as $s$ increases, the average persistence
time (in generations) of the mutation in the population goes below one
generation, i.e. death of the carrier of the \emph{de novo} mutation. In this
hypothetical limit, each occurrence of a very harmful mutation nearly acts like
an instantaneous death that in effect is just a smaller population size. One
way to test this hypothesis is to look to see if there is a systematic positive
relationship across models between average selection coefficient and $\pi_0$,
which is includes the drift-effective population size $N_e$.

We find this is the case for all of our CADD 6\% models. Across every
population, average selection was about $7.1$ times larger using the default
grid, and $\pi_0$ was $5.6\%$ larger. There was no similar consistent change in
mutation rate estimates among populations. In the CADD 6\% model, genome-wide
average reduction factor $\bar{B}$ was $\approx 6.1\%$ lower in the default
versus constrained grid. Overall, this suggests that the linked selection
signal alone cannot differentiate very strong selection from a slightly smaller
drift-effective population size.

Despite the strong-selection non-identifiability issue, we were curious how
stable these estimates are across different reference populations. Overall, the
DFE estimates were consistent over all populations and models (Supplementary
Materials Section \ref{supp:fits}). Here, we highlight the Feature Priority
model since though it is poor-fitting, the DFE estimates are more readily
interpretable since it is based on gene features. Figure \ref{fig:figure-3}B
shows consistent DFE estimates across populations, with narrow uncertainty as
estimated by a block jackknife procedure. Coding sequences have a bimodal DFE
consistent with the strong-selection non-identifiability issue. Additionally,
coding sequences have a very uncertain neutral mode in the DFE. This is
expected given the different level of selective constraint between synonymous
and non-synonymous sites.

Additionally, the PhastCons class of this Feature Priority model, which
contains highly conserved non-coding elements, is under strong selective
constraint as expected. Finally, we highlight one result from our PhastCons
Priority annotation model (Figure \ref{fig:figure-3}A bottom row): the DFE
estimate for coding sequences excluding PhastCons regions is estimated as
neutral. This too is expected; the selection signal in coding regions is
absorbed by the PhastCons feature, leaving only conditionally neutral sites.

@@

Early genome-wide classic BGS models fit well, but lead to unusually high
estimates of the mutation rate \parencite{McVicker2009-ax}. This lead to the
hypothesis that these models could be absorbing the signal of positive
selection \parencite{Enard2014-kz}, though other work has found a limited role
for hitchhiking \parencite{Pickrell2009-tt,Hernandez2011-gs,Murphy2022}. Still,
a central benchmark of fitting genome-wide models is that mutation rate
estimates are in accordance with pedigree-based estimates (XXX).

We find across all populations, our mutation rate estimates from CADD-based
models are roughly concordant with pedigree-based estimates (Figure
\ref{fig:figure-4}A), consistent with recent work \parencite{Murphy2022-sj}.
Our full-track CADD 6\% model estimates the mutation rate as $\widehat{\mu} =
1.46 \times 10^{-8}$ for YRI, $1.53 \times 10^{-8}$ for CEU, and $1.51 \times
10^{-8}$ for CHB reference samples (Supplementary Table \ref{supp:tbl-r2}). As
expected, the sparse-track CADD model mutation rate estimates are identical
between the B' and classic BGS methods (Figure \ref{fig:figure-4}A top row).

However, mutation rate estimates for feature-based annotation models show
several issues. First, mutation rate estimates under our implementation of
classic BGS theory are an order of magnitude below the expected range (Figure
\ref{fig:figure-4}A top row). We observe similar behavior when we use the
classic BGS model to fit full-coverage annotation models (Figure
\ref{fig:figure-4}A bottom row). This behavior is consistent with classic BGS
theory being unable to fit the DFE to features under weak constraint (e.g.
introns, UTRs, and the ``other" feature), and consequently severally
underestimating the mutation rate.

Second, we noticed that across all populations and sparse/full tracks, the CADD
6\% model consistently led to slightly higher mutation rates than the CADD 8\%
model (Figure \ref{fig:figure-4}A bottom row; Supplementary Table
\ref{supp:tbl-r2}). This pattern was observed in Murphy et al. too (2023;
Appendix 1, Figure 16). This behavior is consistent with a non-identifiability
issue between a slightly higher per-basepair mutation rate and annotation
tracks that contain more conserved sequence. This is expected from theory,
since both classic BGS and SC16 models only depend on mutation rate through the
compound parameter $\mu L$, where $L$ is the length of the conserved segment.
Even though our method is much more robust to including non-conserved regions
like introns, we still observe this non-identifiability issue.
